Evaluate PEER in each cohort and brain region

### 2020-11-23 combined_analysis/eval_resid_in_each.Rmd
add CTS

```{r CTS.download}
geneExpr.CTS = readRDS( synGet('syn23234833')$path )
```

@@

  # for each cell type
  for( i in length(dimnames(geneExpr)[[2]]) ){

>>>>

```{r CTS.download}
geneExpr.CTS = readRDS( synGet('syn23234833')$path )
ALL_USED_IDs = c(ALL_USED_IDs, 'syn23234833')
```

@@

  # for each cell type
  for( i in 1:length(dimnames(geneExpr)[[2]]) ){
